Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive bipolar disorders diagnosis for GLAD/EDGI prepan

```{r Get PD positive for GLAD/EDGI}

@@

>>>>

```{r Get Personality Disorders positive for GLAD/EDGI}

@@

```{r Get Bipolar Disorders positive for GLAD/EDGI}

GLAD.prepan_BD_positive <- GLAD.prepan %>%
  select(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) %>% 
  filter(mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1)

GLAD.prepan_BD_positive <- GLAD.prepan_BD_positive %>% 
  summarise("Bipolar disorders" = n())
